Synthesizing Quotient Lenses

### 2018-03-06 papers/QuotientLenses/main.tex
A bit more tidying

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{canonizers-outside}
\caption{Quotient Lens with ``Canonizers at the Edges''
\sam{We don't need a general choose function. With QREs the kernel language is
always contained in the whole language so we just use the inclusion as the
choose function.}\bcp{I can fix.}}
\label{fig:attheedges}
\end{figure}

@@

\fi
\section{Synthesizing QRE Lenses}
\label{synth}
Our goal in this section is to demonstrate how to synthesize a quotient lens
$q: c \Leftrightarrow c'$ from the QREs $c, c'$ and a set of input-output pairs
$\{(x_1, y_1), \ldots, (x_n, y_n)\}$ where the $x_i$'s are in $W(c)$ and the
$y_i$'s are in $W(c')$. We wish $q$ to map the equivalence class of $x_i$ to the
equivalence class of $y_i$ and vice versa:
\begin{align*}
q.get(x_i) &\equiv_{c'} y_i \text{, and}\\
q.put(y_i) &\equiv_c x_i
\end{align*}

@@

Optician~\cite{optician} showed that given regular expressions
$R, S$ and a set of input-output pairs $\{(r_1, s_1), \ldots, (r_n, s_n)\}$, if
there is a derivation $\ell : R \Leftrightarrow S$ of a bijective lens that
maps $r_i$ to $s_i$ in the forward direction and $s_i$ to $r_i$ in the backward
direction, then there is an algorithm that computes a bijective lens $\ell' :
R' \Leftrightarrow S'$ such that $R \equiv R'$, $S \equiv S'$, $\ell'$ maps
$r_i$ to $s_i$ in the forward direction and $s_i$ to $r_i$ in the backward
direction, and $\llbracket \ell \rrbracket = \llbracket \ell'
\rrbracket$.

This implies that if there is a derivation $q : c \Leftrightarrow
c'$ of a QRE lens as well as a derivation $\ell : K(c) \Leftrightarrow K(c')$
that is consistent with the canonized examples $\{({x_1}', {y_1}'),
\ldots, ({x_n}', {y_n}')\}$, then we can synthesize a quotient lens $q$ of
type $c \Leftrightarrow c'$ that is consistent with $\{({x_1}', {y_1}'),
\ldots, ({x_n}', {y_n}')\}$. More concretely, in order to synthesize a
quotient lens $q: c \Leftrightarrow c'$, that is consistent with the examples
$\{(x_1, y_1), \ldots, (x_n, y_n)\}$ it suffices to perform the following
procedure:
\begin{enumerate}
  \item
  Compute $K(c)$, $K(c')$,
  \item
  Compute $\{({x_1}', {y_1}'), \ldots, ({x_n}', {y_n}')\}$ where ${x_i}' =
  \canonizer(c)(x_i)$ and ${y_i}' = \canonizer(c')(y_i)$,
  \item
  Synthesize a bijective lens $\ell : K(c) \Leftrightarrow K(c')$ that is
  consistent with the examples $\{({x_1}', {y_1}'), \ldots, ({x_n}',
  {y_n}')\}$
  \item
  Return $q = \kw{rquot}(\kw{lquot}(c, \ell), c') : c \Leftrightarrow
  c'$
\end{enumerate}
For example, recall that in the \bibtex{} to EndNote transformation we had the
QREs \cd{bibtex} and \cd{endnote} describing a \bibtex{} record and an Endnote
record respectively. We also had the example pair \cd{(bib_example ,
end_example)} where

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{canonizers-outside}
\caption{Quotient Lens with ``Canonizers at the Edges''
\sam{We don't need a general choose function. With QREs the kernel language is
always contained in the whole language so we just use the inclusion as the
choose function.}\bcp{Done.  But I wonder if the picture should mention QREs
explicitly, somehow... any ideas?}}
\label{fig:attheedges}
\end{figure}

@@

\fi
\section{Synthesizing QRE Lenses}
\label{synth}
Our goal in this section is to demonstrate how to synthesize a quotient lens
$q: c \Leftrightarrow c'$ from the QREs $c, c'$ and a set of input-output pairs
$\{(x_1, y_1),\allowbreak \ldots,\allowbreak (x_n, y_n)\}$ where the $x_i$'s are in $W(c)$ and the
$y_i$'s are in $W(c')$. We wish $q$ to map the equivalence class of $x_i$ to the
equivalence class of $y_i$ and vice versa:
\begin{align*}
q.get(x_i) &\equiv_{c'} y_i \text{, and}\\
q.put(y_i) &\equiv_c x_i
\end{align*}

@@

Optician~\cite{optician} showed that given regular expressions
$R, S$ and a set of input-output pairs $\{(r_1, s_1),\allowbreak \ldots,\allowbreak (r_n, s_n)\}$, if
there is a derivation $\ell : R \Leftrightarrow S$ of a bijective lens that
maps $r_i$ to $s_i$ in the forward direction and $s_i$ to $r_i$ in the backward
direction, then there is an algorithm that computes a bijective lens $\ell' :
R' \Leftrightarrow S'$ such that $R \equiv R'$, $S \equiv S'$, $\ell'$ maps
$r_i$ to $s_i$ in the forward direction and $s_i$ to $r_i$ in the backward
direction, and $\llbracket \ell \rrbracket = \llbracket \ell'
\rrbracket$.

This implies that if there is a derivation $q : c \Leftrightarrow
c'$ of a QRE lens as well as a derivation $\ell : K(c) \Leftrightarrow K(c')$
that is consistent with the canonized examples $\{({x_1}', {y_1}'),\allowbreak
\ldots,\allowbreak ({x_n}', {y_n}')\}$, then we can synthesize a quotient lens $q$ of
type $c \Leftrightarrow c'$ that is consistent with $\{({x_1}', {y_1}'),
\ldots, ({x_n}', {y_n}')\}$. More concretely, in order to synthesize a
quotient lens $q: c \Leftrightarrow c'$, that is consistent with the examples
$\{(x_1, y_1),\allowbreak \ldots, (x_n, y_n)\}$ it suffices to perform the following
procedure:
\begin{enumerate}
  \item
  Compute $K(c)$, $K(c')$,
  \item
  Compute $\{({x_1}', {y_1}'), \ldots, ({x_n}', {y_n}')\}$ where ${x_i}' =
  \canonizer(c)(x_i)$ and ${y_i}' = \canonizer(c')(y_i)$,
  \item
  Synthesize a bijective lens $\ell : K(c) \Leftrightarrow K(c')$ that is
  consistent with the examples $\{({x_1}', {y_1}'),\allowbreak
  \ldots,\allowbreak ({x_n}', 
  {y_n}')\}$
  \item
  Return $q = \kw{rquot}(\kw{lquot}(c, \ell), c') : c \Leftrightarrow
  c'$
\end{enumerate}
For example, recall that in the \bibtex{} to EndNote transformation we had the
QREs \cd{bibtex} and \cd{endnote} describing a \bibtex{} record and an Endnote
record respectively. We also had the example pair \cd{(bib_example ,
end_example)} where
